Supplementary Information: Improving Monocular Depth Estimation with Global Depth Histogram Matching

### 2019-10-18 paper/cvpr2020/main.tex
Working on supplement, revised get_hist_med to actually get the median.
pass over paper

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{multirow}
\usepackage{float}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}

\usepackage{dblfloatfix}

@@

\graphicspath{{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org
\end{document}
}
}

>>>>

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{multirow}
\usepackage{float}
\usepackage[utf8x]{inputenc}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{dblfloatfix}

@@

\graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

### 2019-10-18 paper/cvpr2020/sections/hardware.tex
Updated all figures with better z correction.
pass over paper

\begin{figure}[t!]
	\centering
  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

@@

As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW. The SPAD records temporal histograms with 16384 bins, each corresponding to a time window of 16~ps. SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels. The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm that only uses the single histogram of the diffused SPAD and compare it with ground truth. Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.

We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
the scanning system using the standard camera calibration toolbox in MATLAB.
Once the SPAD volume has been summed over the spatial dimensions, it is unclear
how to warp the resulting 1D transient to the RGB camera's perspective (in a
single-pixel flash LiDAR setup, the $512 \times 512$ ground truth data is not
available). However, we do shift the 1D transient by the $z$ displacement
between the SPAD and the RGB camera to partially account for this.

%% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
%
%Missing:
%%
%\begin{itemize}
%\item RGB resolution used for MDE
%\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
%\end{itemize}

@@

Using this prototype, we captured a number of scenes as shown in
Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
to have dimensions that are multiples of 32. For DORN only, we further
downsample the image to a resolution of $353 \times 257$. We then feed this RGB
image into the monocular depth estimation algorithm. In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested. Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement. The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).

In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonable well. However, the root mean squared error (RMSE) for these two scenes is relatively high with 2.4--2.9~m (see red/white error maps in Fig.~\ref{fig:results_captured}). The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m. The ``Poster'' scene is meant to confuse the CNN---it shows a flat poster with a printed scene. As expected, the CNN predicts that the statue is closer than the arches in the background, which is incorrect in this case. The proposed method uses the SPAD histogram to correctly flatten the estimated depth map.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured_results_main}
	\caption{Experimental results. For each scene, we record an RGB image (lower left subimages) and a ground truth depth map that is raster-scanned with the SPAD (upper left subimages). A monocular depth CNN often predicts the ordinal depth well (top two scenes), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages) as shown by the error maps and root mean squared error (RMSE) for each example (lower center and right subimages). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

>>>>

\begin{figure}[t!]
	\centering
  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
    camera is used to capture the image used to generate the monocular depth estimate
    (the depth camera is not used).}
  \label{fig:prototype}
\end{figure}

@@

As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.

The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps. The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparison with the captured depth. Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.

We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
the scanning system using the standard camera calibration toolbox in MATLAB.
While the SPAD histogram and RGB image are captured from slightly different viewpoints, we approximately calibrate the SPAD histogram for this by shifting the 1D transient by the calibrated $z$ offset from the RGB camera.
%We use the camera extrinsics to Once the SPAD volume has been summed over the spatial dimensions, it is unclear
%how to warp the resulting 1D transient to the RGB camera's perspective (in a
%single-pixel flash LiDAR setup, the $512 \times 512$ ground truth data is not
%available). However, we do shift the 1D transient by the $z$ displacement
%between the SPAD and the RGB camera to partially account for this.

We re-bin the captured 1D transient for the indoor captured results 
using Equation~\ref{eq:sid_bin_edges} with $K = 600$ bins, and $(\ell, u)=(0.4, 9.)$.
For the outdoor captured result, we use $K=600$ and $(\ell, u)=(0.4, 11)$. 
%% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
%
%Missing:
%%
%\begin{itemize}
%\item RGB resolution used for MDE
%\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
%\end{itemize}

@@

Using the hardware prototype, we captured a number of scenes as shown in
Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
to have dimensions that are multiples of 32. For DORN only, we further
downsample the image to a resolution of $353 \times 257$. We then feed this RGB
image into the monocular depth estimation algorithm. In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested. Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement. The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).

In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonably well. However, the root mean squared error (RMSE) for these two scenes is relatively high ranging from 2.6--3.2~m (see red/white error maps in Fig.~\ref{fig:results_captured}). The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m. The ``Poster'' scene is meant to confuse the CNN---it shows a flat poster with a printed scene. As expected, the CNN predicts that the statue is closer than the arches in the background, which is incorrect in this case. The proposed method uses the SPAD histogram to correctly flatten the estimated depth map.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left subimages). A monocular depth CNN predicts an initial depth map (top middle subimages), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages). As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right subimages). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

### 2019-10-18 paper/cvpr2020/sections/method.tex
pass over paper

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{method.pdf}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. Then we perform exact histogram matching using
  intensity-weighted pixel values on the corrected SPAD data.}
\end{figure}

Monocular depth estimation is a well-explored, yet active area of research (see Sec.~\ref{sec:related}). Any network trained for the MDE task takes as input an RGB image and estimates the depth map of the scene. Our approach augments existing MDE networks but is agnostic to the specific type of depth estimator. Indeed we show in Section~\ref{sec:evaluation} that our histogram matching technique equally improves a variety of different pre-trained estimators. In the remainder of this section, we therefore focus on modeling the image formation of a diffused single-photon avalanche diode (SPAD) and develop an approach to correcting an estimated depth map to match the global scene information captured by the SPAD.

@@

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates the light scattered back from the scene towards the
detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2}  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the
diffuser. In this formulation, we assume that the diffuser spreads light
uniformly over all angles. Each time such a light pulse is emitted into the
scene and scattered back to the detector,
the single-pixel SPAD time-stamps up to one of the returning photons with some
probability. The process is
repeated millions of times per second with the specific number of emitted pulses
being controlled by the repetition rate of the laser.
Each detected
photon arrival event is discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $(n\Delta t, (n+1) \Delta t)$ models the $n^{th}$ time interval of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents ambient background light and false positive detections known as \textit{dark
count}. As derived in previous work, the combination of signal, background, and
noise can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019}, we adopt the term
\textit{transient} for the histogram $h[n]$.

\subsection{Ambient Rejection and Falloff Correction}
Before histogram matching can be applied, the raw SPAD transient is processed in
three stages.

In the first stage, we remove the ambient and dark count photons from the transient. 
We compute an estimate of $b$ by assuming that the first $N$ bins of the SPAD transient
contain only ambient and dark count photons (this is equivalent to assuming the
minimum image distance is larger than $Nc\Delta T/2$) as:
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
We identify the first and last bins $n_{first}$ and $n_{last}$
corresponding to the minimum and maximum scene depths. We do this with a simple
edge thresholding procedure, computing the absolute first difference $d[n] =
\abs{h[n] - h[n+1]}$. If $h[n]$ and $h[n+1]$ are sampled according to $\mathcal{P}(b)$ and $b$ is large, then 
$h[n] - h[n+1]$ is well-approximated with a Gaussian with mean $0$ and variance $2b$.
Therefore, we can extract a candidate edge set $\mathcal{E}$ as:
\begin{equation}
  \mathcal{E} = \mset{n}{d[n] > \beta\sqrt{2\hat b}}.
  \label{eq:edge_set}
\end{equation}
In this work, we use $\beta = 5$, as it gives good results across both simulated
and captured data.
We compute initial estimates $n'_{first} = \min \mathcal{E}$ and
$n'_{last} = \paren*{\max \mathcal{E}} + 1$ respectively. By appealing to Proposition 3 in
\cite{Xin2019} and noting the similarity of our approach to collecting a single
non-line-of-sight SPAD measurement we can conclude that our estimates must be
close to the true values of $n_{first}$ and $n_{last}$.
We refine these estimates by walking them outwards until their bin values drop
below the ambient estimate $\hat b$, resulting in
$\hat n_{first} = \max\paren*{\set{n'_{first}}\cup\mset{n}{h[n] > \hat b, n \leq n'_{first}}}$ and
$\hat n_{last} = \min\paren*{\set{n'_{last}}\cup\mset{n}{h[n] > \hat b, n \geq n'_{last}}}$.
Finally, we reject all photons outside of the valid range by clamping those bins
to 0, and we subtract our ambient estimate from the photons within the valid
range:
\begin{equation}
  h'_{clean}[n] = \begin{cases}
    0 & n < \hat n_{first} \\
    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
    0 & n > \hat n_{last} \\
  \end{cases}.
  \label{eq:h_clean}
\end{equation}

In the second stage, we set 
\begin{equation}
  h_{clean}[n] = h'_{clean}[n] \cdot r_n^2
  \label{eq:h_scaled}
\end{equation}
where $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the depth
corresponding to bin $n$. This compensates for the radiometric falloff in a way
that is consistent with our hardware prototype's falloff model

In the final stage, we re-bin the transient, applying the Spacing-Increasing Discretization
(SID) of \cite{Fu2018} to produce $h_{target}$. This discretization scheme is
exponential rather than linear, allocating more bins to closer distances and fewer
bins to farther distances. The bin edges $t_i$ are given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
This reduces the number of bins in the histogram
matching procedure, giving speedups while maintaining performance. For the
simulated results,
we use $K = 140$ bins, and $(\ell, u) = (0.657, 9.972)$, (these numbers are
inspired by the discretization scheme for the original DORN network in
\cite{Fu2018})
 For the indoor caputred results, we use $K = 600$ bins, and $(\ell, u)=(0.4, 9) + \epsilon$ 
and for the outdoor captured results, we use $K=600$ and $(\ell, u)=(0.4, 11) +
\epsilon$ where $\epsilon \approx 0.094$ is the $z$ offset between the
SPAD and the Kinect (see Hardware for details).

@@

\subsection{Histogram Matching}
% \begin{algorithm}[H]
%  \caption{Exact Histogram Matching} 
%  \label{alg:ehm}
%  \input{sections/figures/exact_hist_matching_pseudo.tex}
% \end{algorithm}
Histogram matching is a procedure that takes a source image and a target
histogram and maps the pixel values of the source image so that the image's
histogram matches the target histogram. Given a single RGB image, we pass it
through an MDE to produce a depth map. In a parallel processing step,
we compute an estimate $W$ of the scene albedo using an intrinsic imaging method and
take the color channel of the resulting albedo image that corresponds to the
wavelength of the laser illumination.
We then compute a weighted histogram $h_{source}$ of the depth map $\hat z_0$ where the
per-pixel weights are given by $W$, and the bin edges are given by the SID
discretization algorithm in \cite{Fu2018}.

We match the histogram $h_{source}$ to $h_{target}$ using the method of
\cite{Morovic2002}. We compute a pixel movement
matrix $T$ such that $T[m, n]$ is the amount of mass that must be moved from $h_{source}[m]$
to $h_{target}[n]$. We do so using the procedure outlined in \ref{alg:ehm}

\begin{algorithm}[H]
 \caption{Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
  \Procedure{FindMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

Finally, once we have obtained $T$, for a pixel $z_0[i, j]$ in bin $k$, we sample the new bin from the
distribution $T[k, :]/\sum_{n=1}^NT[k,n]$ (which is a distribution over target
depth bins $1,\ldots,N$) to get the bin of $\hat z[i,j]$. We can then apply the
standard SID decoding procedure to get the depth corresponding to that bin
\textcolor{red}{Does the above seem reasonable to include? Not sure if the
  pseudocode is helpful/necessary or not.}
%\subsection{Implementation Details}
%For the Monocular Depth Estimator, we use pretrained versions of the
%the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
%The exact histogram matching method is as described in \cite{}.

>>>>

In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD). We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the diffused SPAD.

@@

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates light scattered back from the scene onto the detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
diffused light, and we assume that the light is diffused uniformly over the
scene points. Each time such a light pulse is emitted into the scene and
scattered back to the detector, the single-pixel SPAD time-stamps up to one of
the returning photons with some probability. The process is repeated millions of
times per second with the specific number of emitted pulses being controlled by
the repetition rate of the laser.  Each detected photon arrival event is
discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $(n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents background detections from ambient light and false positive detections known as \textit{dark
count}. As derived in previous work, the combination of signal and background
can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, we adopt the term
\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{method.pdf}
  \caption{\textbf{Overview of processing pipeline} The processing pipeline uses
      the input SPAD measurements and an RGB image to produce an accurate depth
      map. The SPAD measurements are pre-processed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed SPAD measurements to
      calculate a histogram matching matrix which is used to output the corrected depth map.
  }
  \label{fig:pipeline}
\end{figure}

\subsection{Ambient Rejection and Falloff Correction} Before performing
histogram matching, we apply three pre-processing steps to (1)
remove background counts from the transient, (2) compensate for distance
falloff effects, and (3) re-bin the histogram to improve relative accuracy
with increasing distance. An overview of the processing pipeline, including
these preprocessing steps and the histogram matching procedure is depicted in
Figure~\ref{fig:pipeline}.

In the first step, we remove the background counts from the
transient by initally estimating the average amount of background counts
in each time bin. For nearly all natural scenes, the closest objects to the
camera are a finite distance away, and so the first bins of the SPAD
measurement contain only background counts without any backscattered
signal. We can therefore estimate the
average number of background and noise counts $\hat{b}$ as 
%
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
%
where we choose the number of bins $N$ to correspond to time
values before the backscattered signal arrives.

While simply subtracting $\hat{b}$ from the measurements would remove many of
the background counts, a large number of bins containing only background counts would still
have non-zero values, resulting in a skewed
estimate after applying histogram matching.  Instead, we estimate the temporal
support of histogram bins containing signal photons (\ie the range of depths the
scene) and only subtract $\hat{b}$ from these bins. We assume that other
histogram bins contain only background counts that can be discarded.

Specifically, we identify the first and last bins that record backscattered signal
photons by locating discontinuities in the recorded counts~\cite{Xin2019}. An initial spike in
the measurements at bin $n_\text{first}$ results from the onset of backscattered signal from the closest
object, and a steep dropoff occurs after bin $n_\text{last}$ after backscattered photons from the
furthest object are recorded. 
We estimate $n_\text{first}$ and $n_\text{last}$ by calculating  
first order differences of the histogram $d[n] = \abs{h[n] - h[n+1]}$. 
For a moderate number of background counts, the variance of $h[n] - h[n+1]$ can be approximated  
as a Gaussian with mean $0$ and variance $2b$, and we identify candidate discontinuities
$\mathcal{E}$ with a threshold on the measured differences:
%
\begin{equation}
  \mathcal{E} = \mset{n}{d[n] > \beta\sqrt{2\hat b}}.
  \label{eq:edge_set}
\end{equation}
We find that $\beta = 5$ yields good results across both simulated and captured
data.

Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
Then, we refine these estimates by selecting the closest bins that remain above
a threshold $\tau$ such that
\begin{equation}
    \begin{split}
        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
            \cdots, h[n'_\text{first}] > \tau\}\\
        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
    \cdots, h[n+1] > \tau, h[n] > \tau\}.
    \end{split}
\end{equation}
The remaining ambient counts are discarded by settings the recorded counts to
zero for all bins where $n < n_\text{last}$ and $n > n_\text{last}$.

%Finally, we reject all photons outside of the valid range by
%clamping those bins to 0, and we subtract our ambient estimate from the photons
%within the valid range:
%\begin{equation}
%  h'_{clean}[n] = \begin{cases}
%    0 & n < \hat n_{first} \\
%    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
%    0 & n > \hat n_{last} \\
%  \end{cases}.
%  \label{eq:h_clean}
%\end{equation}

In the second step, we compensate for distance falloff effects by multiplying the histogram
by distance-dependent scaling factor,
\begin{equation}
    h'[n] = h[n] \cdot r_n^2.
  \label{eq:h_scaled}
\end{equation}
Here, $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our hardware prototype.

Last, we re-bin the transient so that the bin widths increase for increasingly
distant objects. We select the Spacing-Increasing Discretization
(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
exponential function, allocating more bins to closer distances and fewer
bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
This rebinning procedure allows us to use a reduced number of bins in the histogram
matching procedure, reducing computation time while maintaining accuracy. For
the simulated results we follow Fu et al.\ and use $K = 140$ bins with $(\ell, u)
= (0.657, 9.972)$~\cite{Fu2018}. The output of the rebinning procedure is the
target histogram $h_\text{target}$ which we use for histogram matching.

@@

\subsection{Histogram Matching}
% \begin{algorithm}[H]
%  \caption{Exact Histogram Matching} 
%  \label{alg:ehm}
%  \input{sections/figures/exact_hist_matching_pseudo.tex}
% \end{algorithm}
Histogram matching is a procedure that adjusts pixel values from an input image
so that the image histogram matches a target histogram. We apply this procedure
to match the histogram of an input depth map, obtained from an MDE, to the
post-processed target histogram $h_\text{target}$ from the SPAD.

The MDE cannot be directly histogram-matched to the target histogram
because the target histogram incorporates the spatially varying reflectance of
the scene. To account for reflectance in the histogram matching procedure,
we use the normalized image color channel closest to the laser wavelength as an
estimate of the reflectance and compute a reflectance-weighted depth histogram
$h_\text{source}$;
instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
at the corresponding depth, we add the estimated reflectance value of the pixel
to the histogram bin.

We match the histogram $h_{source}$ to $h_{target}$ using the method of
Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement
matrix $T$ such that $T[m, n]$ is the fraction of $h_{source}[m]$ that should be
moved to $h_{target}[n]$. The details of this procedure are outlined in
Algorithm~\ref{alg:ehm}. Intuitively, the procedure starts from the first bin of the
source histogram and distributes its contents to the first bins of the target
histogram, with successive source histogram bins being shifted to successive
target bins in sequence.

Finally, we use the movement matrix $T$ to shift the pixels of the MDE depth map
to match the global depth of the target histogram. For a depth map pixel with
depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
case where a single input depth bin of the MDE is mapped to
multiple output bins~\cite{Morovic2002}.
%
\begin{algorithm}[H]
 \caption{Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
  \Procedure{FindMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
%

%\subsection{Implementation Details}
%For the Monocular Depth Estimator, we use pretrained versions of the
%the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
%The exact histogram matching method is as described in \cite{}.

### 2019-10-18 paper/cvpr2020/supplement.tex
pass over paper

\graphicspath{{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}

>>>>

\graphicspath{{"figures/"}{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
